---
title: "Untitled"
author: "Hua Ji"
date: "4/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load_tidy_package}
library(tidyverse)
```

```{r, load_caret_package}
library(caret)
```

## Read training data

The training data set is read in the code chunk below assuming you have downloaded the data from Canvas.  

```{r, read_data_01}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
```

## Regression problem

The data associated with the regression task is created below. Note that the log-transformed response is calculated and assigned to the variable `y`.  

```{r, reg_01}
dfii <- df_all %>% 
  mutate(y = log(response)) %>% 
  select(region, customer, starts_with('x'), y)
```

```{r, reg_02}
my_ctrl_regress <- trainControl(method = 'repeatedcv', number = 5, repeats = 3)
```

Next, define the primary performance metric of the model.  

```{r, reg_03}
my_metrics_regress <- 'RMSE'
```


```{r, reg_04a}
my_regress_method <- 'svmRadial'
```
  

```{r, reg_04}
set.seed(2022)
fit_svm <- train (y~.,
                     data = dfii,
                     method = my_regress_method,
                     preProcess = c("center", "scale"),
                     metric = my_metrics_regress,
                     trControl = my_ctrl_regress)
```


```{r, reg_05}
fit_svm
```

## Classification problem

```{r, class_01}
dfiiiD <- df_all %>% 
  mutate(outcome = factor(outcome, 
                          levels = c("event", "non_event"))) %>% 
  select(region, customer, starts_with('x'), outcome)
```


### Accuracy

The code chunk below specifies the resampling scheme that we will use for the model associated with the Accuracy metric.  

```{r, acc_01}
my_ctrl_acc <- trainControl(method = 'repeatedcv', number = 5, repeats = 3)
```

Next, define the primary performance metric.  

```{r, acc_02}
my_metrics_acc <- "Accuracy"
```


```{r, acc_03}
my_binary_method <- 'glmnet'
```



```{r, acc_04}
set.seed(2022)
       fit_Enet<- train(outcome ~ .,
                        data = dfiiiD,
                        method = my_binary_method,
                        preProcess = c('center', 'scale'),
                        metric = my_metrics_acc,
                        trControl = my_ctrl_acc)
```


```{r, acc_05}
fit_Enet
```

```{r, hold_01}
holdout <- readr::read_csv('final_project_holdout_inputs.csv', col_names = TRUE)
```
```{r, hold_04}
holdout_inputs <- holdout %>% 
  select(-rowid)
```

## Compile predictions

```{r, compile_01}
my_preds <- tibble::tibble(
  y = predict(fit_svm, newdata = holdout_inputs),
  outcome = predict(fit_Enet, newdata = holdout_inputs)
) %>% 
  bind_cols(
    predict(fit_Enet, newdata = holdout_inputs, type = 'prob') %>% 
      select(probability = event)
  ) %>% 
  tibble::rowid_to_column('id')
```


A glimpse of the predictions is shown below.  

```{r, compile_02}
my_preds %>% glimpse()
```

The head of the compiled predictions is shown below.  

```{r, compile_03}
my_preds %>% head()
```

```{r, compile_04}
my_preds %>% 
  readr::write_csv('HoldoutTest.csv', col_names = TRUE)
```

