---
title: "Final Project for PPG PartII : Regression-iiA"
author: "Hua Ji"
date: "4/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
The `tidyverse` and `caret` packages are loaded below.

```{r, load_packages}
library(tidyverse)
library(caret)
```

## Read and prepare data

The code chunk below reads in the `df_all` data and displays 

```{r, read_data}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
df_all %>%glimpse()
```

## Added log-transformed response

```{r}
log_all<-df_all %>%mutate(logresponse =log(response))%>%select(!c(rowid, response,outcome))
log_all%>%glimpse()
```


###Models

##Categorical variables only – linear additive

```{r}
mod1<-lm(logresponse~region+customer,data =log_all)
mod1%>%summary()
```


```{r}
mod1 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```


##Continuous variables only – linear additive

```{r}
mod2<-lm(logresponse~.-region-customer,data =log_all)
summary(mod2)
```


```{r}
mod2 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```


##All categorical and continuous variables – linear additive

```{r}
mod3 <-lm(logresponse~.,data =log_all)
summary(mod3)
```


```{r}
mod3 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```
##Interact region with continuous inputs, do not include customer
```{r}
mod4<- lm(logresponse ~ region * (.-region), data = log_all %>% select(!c( "customer" )))
summary(mod4)
```

```{r}
mod4 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```

##Interact customer with continuous inputs, do not include region

```{r}
mod5<- lm(logresponse ~ customer * (.-customer), data = log_all %>% select(!c( "region")))
summary(mod5)
```

```{r}
mod5 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```


##All pairwise interactions of continuous inputs, do not include categorical inputs

```{r}
mod6<- lm(logresponse ~ (.)^2, data = log_all %>% select(!c( "customer","region")))
summary(mod6)
```

```{r}
mod6 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```

##Natural splines interaction

```{r}
mod7<- lm(logresponse ~ splines::ns(xb_04,5)*splines::ns(xn_05,5), data = log_all)
summary(mod7)
```


## categorical variables and continuous variables interactions

```{r}
mod8<- lm(logresponse ~(.- region - 
    customer)*(region+customer), data = log_all)
summary(mod8)
```

## Quadratic and region interactions.

```{r}
mod9<- lm(logresponse ~ customer*region, data = log_all )
summary(mod9)
```



###Model comparison
Extract multiple performance metrics for each model.
```{r}
extract_metrics <- function(mod, mod_name)
{
  broom::glance(mod) %>% 
    mutate(model_name = mod_name)
}

model_results <- purrr::map2_dfr(list(mod1, mod2, mod3, mod4,
                                      mod5, mod6, mod7, mod8,
                                      mod9),
                                 sprintf("mod-%02d", 1:9),
                                 extract_metrics)

```

Print the R-squared associated with each model. The models are ordered by decreasing R-squared.
```{r}
model_results %>% 
  select(r.squared, model_name) %>% 
  arrange(desc(r.squared))
```
we can visualize the training set R-squared values. 

```{r}
model_results %>% 
  ggplot(mapping = aes(x = r.squared, y =model_name )) +
  geom_linerange(mapping = aes(xmin = 0,
                               xmax = r.squared)) +
  geom_point(size = 4.5) +
  labs(x = '') +
  theme_bw()

```

Let’s compare the performance rankings between the 9 models based on AIC and BIC

```{r}
model_results %>% 
  select(model_name, r.squared,AIC, BIC) %>% 
  pivot_longer(!c("model_name")) %>% 
  mutate(model_id = stringr::str_extract(model_name, "\\d+")) %>% 
  ggplot(mapping = aes(x = model_id, y = value)) +
  geom_point(size = 3.5) +
  facet_wrap(~name, scales = "free_y") +
  labs(x = '') +
  theme_bw()
```
Based on the AIC,BIC, r.squared results, I choose mod3 as the best model. 
The top 3 models are mod8,mod3, and mod4.

##Coefficient summaries for mod8.

```{r}
mod8 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```

##Coefficient summaries for mod3.
```{r}
mod3 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```
##Coefficient summaries.

```{r}
mod4 %>% 
  coefplot::coefplot() +
  theme_bw() +
  theme(legend.position = 'none')
```

The distribution tendency of the coefficient summaries of mod3 and mod4 are similiar, but mod8's is a little different.
It seems that xb-04,xn-7,xn-08,regionZZ and region YY are important inputs. 
