---
title: "PartIIC"
author: "Hua Ji"
date: "4/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
The `tidyverse` and `caret` packages are loaded below.

```{r, load_packages}
library(tidyverse)
library(caret)
```

## Read and prepare data

The code chunk below reads in the `df_all` data and displays 

```{r, read_data}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
df_all %>%glimpse()
```

## Added log-transformed response

```{r}
log_all<-df_all %>%mutate(logresponse =log(response))
log_all%>%glimpse()
```

```{r,eval=TRUE}
mod4<- lm(logresponse ~region* (.-region), data = log_all %>% select(!c("rowid", "customer", "response","outcome")))
```


```{r,eval=TRUE}
mod3<- lm(logresponse ~., data = log_all %>% select(!c("rowid", "customer", "response","outcome","region")))
```

```{r,eval=TRUE}
broom::glance(mod3)
broom::glance(mod4)
```

```{r}
viz_grid <- expand.grid(xb_04 =seq(-3.2,3.2,length.out=101),
                        xn_07=seq(-3,3, length.out=6),
                        xb_01=0,
                        xb_02=0,
                        xb_03=0,
                        xb_05=0,
                        xb_06=0,
                        xb_07=0,
                        xb_08=0,
                        xn_01=0,
                        xn_02=0,
                        xn_03=0,
                        xn_04=0,
                        xn_05=0,
                        xn_06=0,
                        xn_08=0,
                        xa_01=0,
                        xa_02=0,
                        xa_03=0,
                        xa_04=0,
                        xa_05=0,
                        xa_06=0,
                        xa_07=0,
                        xa_08=0,
                        xw_01=0,
                        xw_02=0,
                        xw_03=0,
                        xs_01=0,
                        xs_02=0,
                        xs_03=0,
                        xs_04=0,
                        xs_05=0,
                        xs_06=0,
                        region="XX",
                        customer="A",
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()
viz_grid%>%glimpse()
```

```{r, make_tidy_predict_function}
tidy_predict <- function(mod, xnew)
{
  pred_df <- predict(mod, xnew, interval = "confidence") %>% 
    as.data.frame() %>% tibble::as_tibble() %>% 
    dplyr::select(pred = fit, ci_lwr = lwr, ci_upr = upr) %>% 
    bind_cols(predict(mod, xnew, interval = 'prediction') %>% 
                as.data.frame() %>% tibble::as_tibble() %>% 
                dplyr::select(pred_lwr = lwr, pred_upr = upr))
  
  xnew %>% bind_cols(pred_df)
}
```

```{r, solution_02b, eval=TRUE}
pred_lm_3 <- tidy_predict(mod3,viz_grid)
pred_lm_4 <- tidy_predict(mod4,viz_grid)
```

Create separate code chunks for visualization of mod3. 
```{r}
pred_lm_3%>%ggplot(mapping = aes(x=xb_04))+
  geom_ribbon(mapping = aes(ymin=pred_lwr, ymax=pred_upr),fill="orange")+
  geom_ribbon(mapping =aes(ymin=ci_lwr,ymax=ci_upr),fill="grey")+
  geom_line(mapping = aes(y=pred))+
  facet_wrap(~xn_07)
```


Create separate code chunks for  visualization of mod4. 
```{r}
pred_lm_4%>%ggplot(mapping = aes(x=xb_04))+
  geom_ribbon(mapping = aes(ymin=pred_lwr, ymax=pred_upr),fill="orange")+
  geom_ribbon(mapping =aes(ymin=ci_lwr,ymax=ci_upr),fill="grey")+
  geom_line(mapping = aes(y=pred))+
  facet_wrap(~xn_07)
```

The above graphs showed that the predictive trends are consistent between the 2 selected generalized linear models.